Manuscript_draft

### 2021-03-06 manuscript_draft.Rmd
growth dominance stats

    # Calculate Growth Dominance statistic
    gd.stats<-
      gd.cumu.Inc %>% 
      mutate(GDS=(Cumu.Prop.Inc+lag(Cumu.Prop.Inc,default=0))*(Cumu.Prop.BA-lag(Cumu.Prop.BA,default=0))) %>% 
      ungroup() %>% 
      group_by(Plot,Year) %>% 
      summarise(GDS=1-sum(GDS))

    gd.stats %>% 
      ggplot()+
      aes(x=Year,y=GDS)+
      geom_point()+
      facet_wrap(~Plot)

>>>>

    # Calculate Growth Dominance statistic
    gd.stats<-
      gd.cumu.Inc %>% 
      mutate(GDS=(Cumu.Prop.Inc+lag(Cumu.Prop.Inc,default=0))*(Cumu.Prop.BA-lag(Cumu.Prop.BA,default=0))) %>% 
      ungroup() %>% 
      group_by(Plot,Year) %>% 
      summarise(GDS=1-sum(GDS)) %>% 
      left_join(plotDat,by="Plot")

    gd.stats %>% 
      filter(Year=="1994") %>% 
      ggplot()+
      aes(x=Pre.Harvest,y=GDS)+
      geom_point()
